---
title: "FDOH UF Clinic Evaluation Update"
author: "Joe Brew"
date: "1 July 2015"
output: rmarkdown::tufte_handout
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA}
#####
# LIBRARIES
#####
library(knitr)
library(dplyr)
library(ggplot2)
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = NA)
#####
# DIRECTORY INFO
#####
if(Sys.info()['sysname'] == 'Windows'){
  code_dir <- 'C:/Users/BrewJR/Documents/fdoh/public/uf_clinic/'
  data_dir <- 'E:/fdoh/private/uf_clinic/'
} else {
  code_dir <- '/home/joebrew/Documents/fdoh/public/uf_clinic/'
  data_dir <- '/media/joebrew/JB/fdoh/private/uf_clinic/'
}
#####
# READ IN
#####
setwd(data_dir)
load('checkpoint.RData')

```


# Summary

\newthought{I have gathered}, cleaned and organized data from the following two sources:   

1. UF's Student Health Care Center Clinic \marginnote{(SHCC)}   
2. Florida Department of Health \marginnote{(FDOH)} in Alachua's STI testing program embedded at the UF SHCCC 


\noindent This document provides a summary of the data, as well as next steps in the evaluation effort.

# Data summary

## FDOH  

```{r, fig.margin = TRUE}
g <- ggplot(data = fdoh)
g + geom_density(aes(date), fill = 'blue', alpha = 0.5) +
  theme_bw() +
  xlab('Date') +
  ylab('Density') +
  ggtitle('FDOH-administered tests at UF SHCC') +
  theme(text = element_text(size = 8),
        axis.text.x = element_text(angle = 90, size = 4))

  
```

The FDOH testing data ranges from `r format(min(fdoh$date), '%B %d, %Y')` through `r format(max(fdoh$date), '%B %d, %Y')`.  For the sake of this analysis, test results are ignored, and we insead concentrate exclusively on the number of tests over time (as a proxy measure for general test "availability", the assumption being that the more "available" testing is perceived to be, the more tests will be performed).


A\marginnote{(The likely average daily number of tests is higher, as this does not take into account holidays and university vacations.)} total of `r nrow(fdoh)` tests were performed, and the testing rate has remained stable over the last few years (after adjustment for expected academic seasonality), at an average of `r round(nrow(fdoh) /  as.numeric(max(fdoh$date) - min(fdoh$date))* (7/5), digits = 2)`.



## UF  

The UF dataset goes back further in time, ranging from December 2005 through March 2015.  It includes _all_ diagnoses (not just STI's).  After dipping to a low in 2010, the rate at which the SHCC sees patients appears to have increased steadily since then.

```{r, fig.margin = TRUE}
uf$date <- as.Date(paste0(uf$year, '-',
                             uf$month, '-01'))
g <- ggplot(data = uf)
g + geom_density(aes(date), fill = 'blue', alpha = 0.5) +
  theme_bw() +
  xlab('Date') +
  ylab('Density') +
  ggtitle('FDOH-administered tests at UF SHCC') +
  theme(text = element_text(size = 8),
        axis.text.x = element_text(angle = 90, size = 4))

```


## Other data

To make our analysis meaningful, we'll need to calculate both the cost of those `r nrow(fdoh)` tests, as well as the opportunity costs of having spent those dollars in other venues.  We'll also require statewide STI trends and cost data from the UF end.

\newpage

# Next steps

## Done  

I've contacted Randy Jarmon regarding the necessary financial data.  Following the delivery of financial data from Randy Jarmon, I'll 


## To do

I'll get back in touch with Guy Nicolette regarding the exact cost of STI testing for the UF SHCC, and will follow up with Randy regarding FDOH cost data.   


\noindent I'll gather and clean STI and population data for Florida from Florida charts.     

\noindent Once all the data is in place, I'll conduct a cost-utility and cost-effectiveness analysis.  The final product will be an internal-facing report, for distribution at administration's discretion, and an optional external-facing article.  

```{r, fig = TRUE}
ts$date <- as.Date(paste0(ts$year, '-',
                             ts$month, '-01'))
g <- ggplot(data = ts) 
g + geom_smooth(aes(x = date, y = sti)) +
  theme_bw() +
  xlab('Year') +
  ylab('STI diagnoses / tests') +
  ggtitle('STI diagnoses at SHCC (blue = diagnoses; orange = tests)') +
  theme(text = element_text(size = 8),
        axis.text.x = element_text(angle = 90, size = 4)) +
  geom_bar(aes(x = date, y = n_tests), stat = 'identity', col = 'orange', fill = 'orange', alpha = 0.5)
```

